Influences of GDP in the U.S

### 2022-11-12 Manuscript/manuscript.tex
commit

\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{multirow}
\usepackage{setspace}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

@@

@@

When applying multiple linear regression to the data set, all independent variables were included in the intital model.
The model was built using the variables TPEC, POP, TCMR, DPI, UNRATE and BSLP from the training dataset.

>>>>

\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{float}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

@@

% explain VIF and AV plots

@@

When applying multiple linear regression to the data set, all independent variables were included in the intital model.
Model 1 was built using the variables TPEC, POP, TCMR, DPI, UNRATE and BSLP from the training dataset. 
The equation used for this model is as follows:

\begin{equation}
  GDP = \beta_0 + \beta_1 TPEC + \beta_2 TCMR+ \beta_3 DPI + \beta_4 UNRATE + \beta_5 BSPL
\end{equation}

Summary statistics for this model are as follows:

\begin{figure}[H]
  \centering
  \includegraphics[width = \textwidth]{mod1output}
  \caption{This figure shows the output from R for the summary statistics for Model 1}
\end{figure}
